%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue,
    filecolor=blue
}
\usepackage[ocgcolorlinks]{hyperref}
% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     urlcolor=blue,
%     citecolor=blue,
%     filecolor=blue,
%     linkbordercolor=blue,
%     urlbordercolor=blue,
%     citebordercolor=blue,
%     filebordercolor=blue
% }
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item 
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingwithout}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
% \vspace{0.5em}
%   \textbf{{\LARGE Khushdeep Jain}} & Email: \href{khushdeep.jain@gmail.com}{khushdeep.jain@gmail.com}\\
  
%   \href{https://www.linkedin.com/in/khushdeep-jain-203783203/}{LinkedIn: https://www.linkedin.com/in/khushdeep-jain-203783203/} & Mobile:~+91-9015111425\\
%   \href{https://github.com/Deborg201}{Github: https://github.com/Deborg201} \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Khushdeep Jain} \\ \vspace{1pt}
    \small +91 90151-11425 $|$ \href{mailto:khushdeep.jain@gmail.com}{\underline{khushdeep.jain@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/khushdeep-jain-203783203/}{\underline{LinkedIn}} $|$
    \href{https://github.com/Deborg201}{\underline{Github}}
\end{center}

%-----------EDUCATION-----------------
\section{\textbf{Education}} \vspace{0.6em}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NIT Hamirpur}{Himachal Pradesh, India}
      {Bachelor of Technology - Electronics \& Communication Engineering; CGPA: 8.8} {12/2020 - 07/2024}
      \vspace{5pt}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Data Structures, Analysis Of Algorithms, Databases, OS,Neural Networks \& Fuzzy Logic, Microprocessors, Micro Controllers, Network, Computer Organisation \& Architecture, ARM Architecture}}}
    \resumeSubHeadingListEnd
	    
\vspace{-7pt}
\section{\textbf{Skills Summary}} \vspace{0.6em}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~ {\hspace{5.5em}}C++, Python, HTML, CSS, JavaScript, SQL}
	\resumeSubItem{Frameworks \& Libraries}{~~React, Redux, NextJS , 
 NodeJS, Express, MongoDB, jQuery, Mongoose, Tailwind CSS}
	\resumeSubItem{Tools}{~~~~~~~~{\hspace{7.5em}}GIT, Postman, MongoDB Compass, MySQL, VS Code, NPM}
	\resumeSubItem{Platforms}{~~~~~{\hspace{6.3em}}Linux, Web, Windows, Arduino, AWS, GCP, IBM Cloud}
	\resumeSubItem{Soft Skills}{~~~~{\hspace{6.5em}}Leadership, Event Management, Public Speaking, Time Management, Communication}

\resumeSubHeadingListEnd
\vspace{-0.8pt}
\section{\textbf{Experience}}

  \resumeSubHeadingListStart
  \vspace{0.5em}
  \resumeSubheading
		{Qloron Pvt. Ltd. }{Remote}
		{Full Stack Web Developer Intern (Full-time)}{01/2023 - 03/2023}\newline
{}
		\resumeItemListStart
  \vspace{-0.5em}
            \resumeItem{}{Served as a Full Stack Developer, demonstrating expertise in various technologies.}
            \resumeItem{}{Delivered multiple projects successfully within stipulated timelines, ensuring on-time completion.}
            \resumeItem{}{Analyzed, updated, and maintained existing code-bases to optimize functionality and performance.}
            \resumeItem{}{Demonstrated strong project management skills by overseeing project timelines and ensuring timely submissions.}
            
		\resumeItemListEnd
  % \vspace{3pt}


  %   \resumeSubheading{Bharat Electronics Limited (PSU ,Govt. of INDIA)}{Onsite}
  %   {Intern (Full-time)}{12/2022 - 01/2023}
  %   \resumeItemListStart
  %       \resumeItem{}{Contributed valuable services to the organization during my tenure as an ECE Intern.}
  %       \resumeItem{}{Conducted in-depth observation and analysis of the entire lifecycle of Classroom Jammers}
  %       \resumeItem{}{Gained valuable insights into Software-Defined Radios (SDRs) through hands-on experience and research.}
  %       \resumeItem{}{Developed a profound understanding of the internal workings of a successful, large-scale organization.}
  %     \resumeItemListEnd
\vspace{1.5pt}
%     \resumeSubheading
% 		{Srishtis Engitech Private Limited }{Onsite}
% 		{Intern (Full-time)}{Jun 2022 - Jul 2022}\newline\newline
% {Srishtis Engitech Pvt Ltd is a company responsible for laying down the entire 4G infrastructure for JIO 4G network in densely populated States of Punjab, Haryana \& Chandigarh with an uptime of 95\%.
% I got to chance to carefully observe -} 
% 		\resumeItemListStart
%   \vspace{-0.5em}
%             \resumeItem{}{End to End projects life cycle.}
%             \resumeItem{}{Field visit to understand network structure of 5G upgradation.}
%             \resumeItem{}{Understanding of techno commercial part of ongoing projects.}
%             \resumeSubItem{}{Planning Execution and Understanding of various projects allocated to the company.}
% 		\resumeItemListEnd
% \vspace{3pt}
\resumeSubHeadingListEnd    
%-----------PROJECTS-----------------
\vspace{-1.5pt}
\section{\textbf{Projects}} \vspace{0.6em}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://deborg201.github.io/YouTubeClone/}{MyYouTube} (React, Redux,Testing-Library)}
\resumeItemListStart
 \resumeItem{}{Developed a React and Redux-based Single Page Application (SPA) with seamless routing for a smooth user experience.}
 \resumeItem{}{Implemented advance optimization techniques like 200 ms debouncing for search and caching for enhanced performance.}
 \resumeItem{}{Built support for nested comments to enrich user engagement.}
% \vspace{2pt}
\resumeItemListEnd
\resumeSubItem{\href{https://shareware-pfwj.onrender.com/}{ShareWare} (Javascript, MongoDB, Express, NodeJs, EJS)}
\resumeItemListStart
\resumeItem{}{Established a web platform for users to request and provide items based on their needs.}
\resumeItem{}{Crafted an intuitive UI for easy navigation along with a robust authentication system.}
\resumeItem{}{Leveraged MongoDB as backend database for efficient data storage and retrieval to serve the users effectively.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubItem{\href{https://deborg201.github.io/WonderLand/}{WonderLand} (React,RapidAPI)}
\resumeItemListStart
\resumeItem{}{Created a dependable online platform providing accurate and user-friendly information.}
\resumeItem{}{Integrated multiple APIs from various sources, ensuring seamless collaboration.}
\resumeItem{}{Enhancing the platform by adding features like recommendations, watchlists, and voice search capabilities.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubItem{Save a Tree - (Javascript,NodeJs,Image information Extraction)}{(Work in progress) \newline Helps survey the current rate of afforestation and deforestation without need of physical presence. The user uploads a geotagged pic of a fallen tree and using image information extraction the location is mapped and a database is created. Available space is marked for plantation of new tree or \href{https://worldbiomarketinsights.com/a-liquid-tree-scientists-in-serbia-make-incredible-innovation/}{Liquid3.}  (Feb '23)}
\resumeSubHeadingListEnd
\vspace{-0.3pt}
%\section{Publications}
% \resumeSubHeadingListStart
% \resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
% \vspace{2pt}
% \resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
% \resumeSubHeadingListEnd
% \vspace{-5pt}
%-----------Awards-----------------
\section{\textbf{Honors and Awards}} \vspace{0.6em}
\begin{description}[font=$\bullet$]
\item {SVJN Silver Jubilee Merit Scholarship}
\vspace{-5pt}
\item {Runner's Up at Electrothon 3.0, a national level electrothon conducted by NIT Hamirpur}
\vspace{-5pt}
\item {Academic Excellence Award ~~~~~Felicitated by Shree Ashok Goyal (Chairman, Tirupati Pharmaceuticals) }
\vspace{-5pt}
\item {Academic Excellence Award ~~~~~Felicitated by Dr. SP Singh Oberoi
(Chairman, Apex Group of Companies , Dubai)}
\vspace{-5pt}
\item {Academic Excellence Award ~~~~~Felicitated Mr Arjun Juneja (COO, Mankind Pharmaceuticals)}
\vspace{-5pt}


\end{description}

\vspace{-0.2pt}
\section{\textbf{Volunteer Experience}} \vspace{0.6em}
  \resumeSubHeadingListStart
    \resumeSubheadingwithout{Google Developers Student Group (Web Team Lead) }{05/2022 - Present}
    \resumeItemListStart
        \resumeItem{}{Collaborated on various projects, contributing to their successful execution and completion.}
        \resumeItem{}{Orchestrated and managed diverse events, including workshops, drawing in 450 plus attendees}
        \resumeItem{}{Demonstrated strong leadership skills by efficiently managing a team of over 100 plus members.}
      \resumeItemListEnd
      \vspace{1.5pt}
    \resumeSubheadingwithout
    {Sustainable Club of NIT Hamirpur SCON}{01/2023 - Present}
    \resumeItemListStart
    
    \resumeItem{}{Organized and delivered training sessions on sustainable practices,impacting a wide audience.}
    \resumeItem{}{Conducted surveys to gather valuable insights.}
    \resumeItemListEnd
      \vspace{1.5pt}
\resumeSubheadingwithout
    {Society for Promotion of Electronics Culture SPEC}{12/2020 - 06/2022}
     \resumeItemListStart
    \resumeItem{}{Hosted national-level hackathon driving 1000 plus students across nation}
    \resumeItem{}{Developed creative solutions for challenges related to college student life.}
    \resumeItemListEnd
\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
   

\resumeSubHeadingListEnd

\end{document}
